\documentclass{resume}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=cyan,
}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\usepackage{enumitem}
\setlist[itemize]{left=0}
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}

\name{Haoxuan (Alex) Zeng} % Name
\address{Chicago, IL} % Address
\address{\small{(847)756-0726 \mid zenghaoxuan72@gmail.com \mid linkedin.com/in/haoxuan$-$zeng \mid github.com/hzeng98}} % Phone number and email and etc

\begin{document}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Work Experience}

\begin{rSubsection}{Bridge Legal, Chicago, IL} {\textit{May 2023 $-$ July 2024}}
{\normalfont{Software Engineer}}

    \item Analyzed user requirements and enhanced the Bridgify system for seamless API integration configuration.
    \item Used Agile methodology to develop a Java-based Uploader, aligning customer data with our formats and uploading it to the database.
    \item Developed a Python script that accelerated the process of mapping customer fields to internal fields by 60\%.
    \item Facilitated customer communication and guided them in configuring Bridgify Automation to deliver retainers to their clients.
    \item Wrote SQL scripts to extract and update daily intake team metrics in Airtable.
    \item Designed a Marketing Operations Dashboard on Looker Studio, customizing tables to align with leadership's requirements.
    \item Utilized Cloud9 and Lambda to develop an automation script for updating data in the Pulse System, resulting in a 20\% improvement in system scalability and efficiency.
    \item Collaborated with colleagues to design a new Integration Platform and develop the Data Config feature.
    \item Automated PDF editing workflows using Python and SQL, increasing efficiency by 100 times and ensuring error-free modifications.
    \item Tested the Fund Management Model within the CRM, identified logic flaws, and collaborated with engineers to resolve these issues, enhancing model accuracy and performance.

\end{rSubsection}

\begin{rSubsection}{Bridge Legal, Chicago, IL} {\textit{March 2023 $-$ May 2023}}
{\normalfont{Engineering Intern}}

    \item Assisted law firms in configuring API integration and troubleshooting to ensure system stability.
    \item Customized Outbound API integration to achieve automated case posting and meet customer needs.
    \item Operated Bridgify CRM proficiently, configured workflows and automation processes, and identified gaps.
    \item Utilized Datagrip to access databases and wrote SQL queries to extract cases for various Mass Tort projects.

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
% SKILL SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Skills}

\begin{rSubsection}{}{}
{} % necessary to maintain the structure

    \item Advanced in \textbf{Python}, \textbf{Java}, \textbf{SQL}, \textbf{JavaScript}
    \item Advanced in \textbf{JSON}, \textbf{HTML5}, \textbf{CSS3}, \textbf{REST APIs}, \textbf{ReactJS}, \textbf{Node.JS}
    \item Advanced in \textbf{Git}, \textbf{POSTMAN}, \textbf{Jupyter Notebook}, \textbf{Anaconda}
    \item Experienced with \textbf{MySQL}, \textbf{PostgreSQL}, \textbf{DataGrip}, \textbf{AWS}, \textbf{Google Cloud Platform}
    \item Advanced in \textbf{Agile} methodology
    \item \textbf{English (Fluent)} and \textbf{Chinese (Native)}

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{Education}

    \item {\bf University of Illinois at Chicago} \hfill {\em Aug 2018 $-$ May 2023}
    \\ Bachelor of Computer Science

\end{rSection}

\end{document}
